%-------------------------
% Resume in Latex
% Author : Devang Dhanuka
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\usepackage[left=0.35in, right=0.4in, top=0.4in, bottom=0.4in]{geometry}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{0pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    {\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-10pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Devang Dhanuka} \\ \vspace{1pt}
    \small +1(908)935-8654 $|$ \href{mailto:ddhanuka1304@gmail.com}{\underline{ddhanuka1304@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/devang1304/}{\underline{linkedin.com/in/devang1304}} $|$
    \href{https://github.com/devang1304}{\underline{github.com/devang1304}}
\end{center}
\vspace{-12pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Research Assistant – Explainable AI (XAI) for Cybersecurity}{Oct 2024 -- Present}
    {Rochester Institute of Technology | Advisor: Prof. Nidhi Rastogi}{Rochester, NY}
    \resumeItemListStart
      \resumeItem{Developed an explainable intrusion detection framework using Temporal Graph Neural Networks (TGNN) on DARPA Trusted Computing datasets, improving transparency of cybersecurity alerts.}
      \resumeItem{Benchmarked explainability methods (GNNExplainer, PGExplainer), analyzing fidelity, stability, and accuracy, and integrated results into interactive SOC dashboards (Streamlit) to enhance analyst decision-making.}
    \resumeItemListEnd

  % \resumeSubheading
  %   {Senior Engineer – Cloud Infrastructure \& Security}{Aug 2020 -- Jun 2023}
  %   {Netwoven Inc.}{Kolkata, India}
  %   \resumeItemListStart
  %     \resumeItem{Automated operational workflows using Power Automate and PowerShell, reducing manual effort by 40\%.}
  %     \resumeItem{Supported large-scale Microsoft 365 and Azure migrations for 3,000+ users, ensuring zero downtime and data integrity.}
  %     \resumeItem{Implemented enterprise-grade identity and security controls (Information Protection, DLP, Intune, Conditional Access) securing 3M+ sensitive records across global supply chains.}
  %     \resumeItem{Designed Power BI dashboards to track compliance posture, license usage, and incident metrics, improving IT governance and reporting efficiency.}
  %   \resumeItemListEnd

\resumeSubheading
  {Senior Engineer – Cloud Infrastructure \& Security}{Aug 2020 -- Jun 2023}
  {Netwoven Inc.}{Kolkata, India}
  \resumeItemListStart
    % \resumeItem{Managed \textbf{Azure resources} for deployment, tagging, and cost optimization, and led \textbf{Microsoft 365 tenant-to-tenant migration} for \textbf{3,000+ users} with zero downtime; implemented \textbf{Information Protection, DLP, Intune, and Conditional Access} to strengthen enterprise data security.}
    \resumeItem{\textbf{Managed Azure resources} for deployment and cost optimization—implemented \textbf{resource tagging}, budgeting, and cost reports to enhance visibility, billing accuracy, and cloud spend governance.}
    \resumeItem{Led \textbf{Microsoft 365 tenant-to-tenant migrations} for \textbf{3,000+ users} with zero downtime, and implemented enterprise-grade controls (\textbf{Information Protection, DLP, Intune, Conditional Access}) to safeguard sensitive data across global organizations.}
    \resumeItem{Automated key \textbf{IT operations workflows} using \textbf{Power Automate} and \textbf{PowerShell} to improve efficiency and reduce repetitive tasks across identity, licensing, and compliance operations.}
    \resumeItem{Supported \textbf{Govern365} (data governance platform) through \textbf{PoCs, customer demos, production deployments}, and adoption initiatives to align compliance frameworks with customer environments.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Evaluation Framework for SOC LLMs} $|$ \emph{OpenAPI, HuggingFace, AWS Bedrock, GCP Vertex AI}}{Jul 2025 -- Present}
    \resumeItemListStart
      \resumeItem{Built a vendor-agnostic benchmark ingesting multi-source logs, normalizing to \textbf{ECS/STIX}, mapping to \textbf{MITRE ATT\&CK}, and evaluating \textbf{proactive (log-driven)} and \textbf{reactive (alert-driven)} SOC workflows across models (Anthropic, OpenAI, Gemini, LLaMA, DeepSeek, Qwen).}
      \resumeItem{Generated reproducible scores for \textbf{detection/triage, IOC extraction, hallucination accuracy, ATT\&CK coverage}, with dashboards reporting \textbf{latency, cost, and explainability}.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Financial Management Hub (Serverless AWS App)} $|$ \emph{AWS, Terraform, Docker, CI/CD}}{Feb 2025 -- Apr 2025}
    \resumeItemListStart
      \resumeItem{Developed a serverless financial tracking app using AWS Amplify, Lambda, and DynamoDB, integrated with Plaid/OpenAI APIs for automated expense insights, achieving 99.99\% availability.}
      \resumeItem{Implemented auto-scaling infrastructure and CI/CD pipelines with Terraform, Docker, and GitHub Actions}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Travel Itinerary Planner with Google ADK Agents} $|$ \emph{Google ADK, Vertex AI, BigQuery}}{May 2025 -- Jun 2025}
    \resumeItemListStart
      \resumeItem{Built a multi-agent planning system leveraging Google ADK; agents ranked attractions, ingested preferences, and generated optimized day-by-day travel itineraries.}
      \resumeItem{Applied orchestration techniques, serverless architecture, and GCP IAM/security policies to deliver a cost-efficient, scalable system.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {MS Data Science}{Aug 2023 -- Dec 2025}
    {Rochester Institute of Technology}{Rochester, NY}
  \resumeSubheading
    {Bachelor of Computer Applications}{Jul 2017 -- Jun 2020}
    {Amity University}{Noida, India}
\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-4pt]
    \item \small \textbf{“Survey Perspective: The Role of Explainable AI in Threat Intelligence.”}\\ Nidhi Rastogi, Devang Dhanuka, \emph{et al.} – Survey study on integrating XAI into SOC workflows.
    \item \small \textbf{“Too Much to Trust? Measuring the Security and Cognitive Impacts of Explainability in AI-Driven SOCs.”}\\ Nidhi Rastogi, Devang Dhanuka, \emph{et al.} – Evaluates explainability methods’ effect on analyst trust and efficiency.
    \item \small \textbf{“Impact of LLMs on Team Collaboration in Software Development."} Devang Dhanuka.
\end{itemize}

\vspace{-12pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-4pt]
    \item \textbf{Programming:} Python, Java, SQL, PowerShell  
    \item \textbf{ML/AI:} PyTorch, TensorFlow, HuggingFace, XAI (LIME, SHAP, GNNExplainer)  
    \item \textbf{Cloud/MLOps:} AWS, GCP, Azure, Terraform, Docker, Kubernetes, CI/CD  
    \item \textbf{Databases/Analytics:} MySQL, PostgreSQL, NoSQL, Pandas, NumPy, PowerBI, Streamlit
\end{itemize}

\end{document}
